---
title: "Master Thesis Simulation: Small-Sample Corrections for LRT in SEM"
subtitle: "Comparing Correction Methods Across Model Complexities"
author: "Your Name"
date: "`r Sys.Date()`"
output:
  html_document:
    toc: true
    toc_float: true
    number_sections: true
    theme: cosmo
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,
                      message = FALSE,
                      warning = FALSE,
                      cache = TRUE)

library(lavaan)
library(semTools)
library(dplyr)
library(tidyr)
library(knitr)
library(progress)
library(ggplot2)

# --- THESIS SIMULATION SETTINGS ---
sample_sizes <- c(25, 50, 75, 100, 150, 200, 300, 1000, 10000)
n_reps       <- 10
alpha        <- 0.05
set.seed(2024)

# --- HELPER FUNCTIONS ---

safe_fit <- function(syntax, data, estimator = "ML", test = NULL, bootstrap = NULL) {
  if (is.null(data)) return(NULL)
  args <- list(model = syntax, data = data, estimator = estimator, warn = FALSE)
  if (!is.null(test))      args$test <- test
  if (!is.null(bootstrap)) args$bootstrap <- bootstrap
  tryCatch(do.call(sem, args), error = function(e) NULL)
}

safe_fm <- function(fit, measure) {
  if (is.null(fit)) return(NA_real_)
  tryCatch(as.numeric(unclass(fitMeasures(fit, measure))), error = function(e) NA_real_)
}

safe_smallN <- function(fit, method) {
  if (is.null(fit)) return(list(chisq = NA_real_, pvalue = NA_real_))
  res <- tryCatch(chisqSmallN(fit, smallN.method = method), error = function(e) NULL)
  if (is.null(res) || length(res) == 0) return(list(chisq = NA_real_, pvalue = NA_real_))
  c_val <- res[["chisq"]]; p_val <- res[["pvalue"]]
  list(
    chisq   = if (length(c_val) == 1) as.numeric(c_val) else NA_real_,
    pvalue  = if (length(p_val) == 1) as.numeric(p_val) else NA_real_
  )
}

safe_reject <- function(p, alpha = 0.05) {
  if (length(p) != 1) return(NA)
  if (is.na(p)) return(NA)
  p < alpha
}
```

# 1. Model Definitions

We simulate data under the Null Hypothesis (H0) at **two levels of model complexity**:

1.  **Simple CFA** (df = 24): 3 latent factors, 9 observed indicators, one factor correlation.
2.  **Complex CFA** (df ~ 120): 6 latent factors, 18 observed indicators, eight factor correlations.

For each model, the fitted model is exactly the model that generated the data. This allows us to calculate **Type I Error rates** (rejection rates) under correctly specified models.

```{r model-definitions}
# ---- Model 1: Simple CFA (3 factors, 9 indicators) ----
simple_cfa_syntax <- '
  f1 =~ x1 + x2 + x3
  f2 =~ x4 + x5 + x6
  f3 =~ x7 + x8 + x9
  f1 ~~ f2
'

# ---- Model 2: Complex CFA (6 factors, 18 indicators) ----
complex_cfa_syntax <- '
  f1 =~ y01 + y02 + y03
  f2 =~ y04 + y05 + y06
  f3 =~ y07 + y08 + y09
  f4 =~ y10 + y11 + y12
  f5 =~ y13 + y14 + y15
  f6 =~ y16 + y17 + y18
  f1 ~~ f2
  f1 ~~ f3
  f1 ~~ f4
  f2 ~~ f3
  f3 ~~ f4
  f4 ~~ f5
  f4 ~~ f6
  f5 ~~ f6
'

# ---- Build model registry ----
models <- list(
  simple_cfa  = list(name = "Simple CFA",
                     description = "3 factors, 9 indicators",
                     syntax = simple_cfa_syntax),
  complex_cfa = list(name = "Complex CFA",
                     description = "6 factors, 18 indicators",
                     syntax = complex_cfa_syntax)
)

# Compute df for each model via a dummy fit
model_info <- list()
for (key in names(models)) {
  m <- models[[key]]
  dummy_data <- simulateData(m$syntax, sample.nobs = 20)
  dummy_fit  <- sem(m$syntax, data = dummy_data, warn = FALSE)
  model_info[[key]] <- list(
    name        = m$name,
    description = m$description,
    syntax      = m$syntax,
    df          = as.integer(safe_fm(dummy_fit, "df")),
    n_indicators = ncol(dummy_data)
  )
}
```

```{r show-model-info, echo=FALSE}
model_summary_df <- data.frame(
  Model = sapply(model_info, function(x) x$name),
  Description = sapply(model_info, function(x) x$description),
  Indicators = sapply(model_info, function(x) x$n_indicators),
  df = sapply(model_info, function(x) x$df)
)
kable(model_summary_df,
      caption = "Two model complexity levels used in the simulation.",
      col.names = c("Model", "Description", "Indicators (p)", "Degrees of Freedom"))
```

# 2. Run Simulation

The simulation is split into **separate cached chunks**, one per correction method. Each chunk loops over all 2 model complexity levels. Results are saved in **per-model RDS files** (e.g., `thesis_sim_base_simple_cfa.rds`) for fault isolation.

Each chunk uses the **same per-iteration seed** (based on a global index) to guarantee identical data generation across all method chunks for a given model/N/replication combination.

Seed strategy:
$$\\text{seed} = 20240000 + (\\text{model\\_offset}) + (\\text{iter\\_index})$$
where `model_offset = (\\text{model\\_rank} - 1) \\times |\\text{sample\\_sizes}| \\times \\text{n\\_reps}`.

## 2.1 Base: Data Generation & Uncorrected LRT

```{r sim-base, results='asis'}
verbose_models <- c("simple_cfa")
total_per_model <- length(sample_sizes) * n_reps

for (model_key in names(models)) {
  info <- model_info[[model_key]]
  syn  <- info$syntax
  model_rank <- which(names(models) == model_key)
  model_offset <- (model_rank - 1) * total_per_model

  cat(sprintf("\\n\\n%s\\n", paste(rep("=", 70), collapse = "")))
  cat(sprintf("  MODEL: %s  (%s)  |  df = %d\\n", info$name, info$description, info$df))
  cat(sprintf("  %d sample sizes x %d replications = %d iterations\\n",
              length(sample_sizes), n_reps, total_per_model))
  cat(sprintf("%s\\n\\n", paste(rep("=", 70), collapse = "")))

  verbose_flag <- model_key %in% verbose_models
  results <- list()
  success_count <- 0
  fail_count <- 0

  pb <- progress_bar$new(
    format = paste0("  [base-", substr(model_key, 1, 6), "] ",
                    "[:bar] :percent | ETA: :eta | Iter :cur/:tot | N=:n | Rep :rep/:reps"),
    total = total_per_model, clear = FALSE, width = 80
  )

  idx <- 0
  prev_n <- NA

  for (n in sample_sizes) {
    if (verbose_flag && (is.na(prev_n) || n != prev_n)) {
      cat(sprintf("\\n========================================\\n"))
      cat(sprintf("  N = %d  |  %d replications  (%d of %d sample sizes)\\n",
                  n, n_reps, which(sample_sizes == n), length(sample_sizes)))
      cat(sprintf("========================================\\n"))
    }
    prev_n <- n

    for (i in 1:n_reps) {
      idx <- idx + 1
      global_seed <- 20240000 + model_offset + idx
      pb$tick(tokens = list(cur = idx, tot = total_per_model,
                            n = n, rep = i, reps = n_reps))

      set.seed(global_seed)
      if (verbose_flag) {
        cat(sprintf("\\n  --- Iter %d/%d  |  N=%d  |  Rep %d/%d  |  seed=%d ---\\n",
                    idx, total_per_model, n, i, n_reps, global_seed))
      }

      sim_data <- tryCatch(simulateData(syn, sample.nobs = n), error = function(e) NULL)

      if (verbose_flag) {
        if (!is.null(sim_data)) {
          cat(sprintf("    Step 1/2 : Generated %d x %d dataset\\n", n, ncol(sim_data)))
        } else {
          cat("    Step 1/2 : Data generation FAILED\\n")
        }
      }

      fit_ml <- safe_fit(syn, sim_data, estimator = "ML")

      if (!is.null(fit_ml)) {
        success_count <- success_count + 1
        if (verbose_flag) cat("    Step 2/2 : ML estimation ........... OK\\n")
      } else {
        fail_count <- fail_count + 1
        if (verbose_flag) cat("    Step 2/2 : ML estimation ........... FAILED\\n")
      }

      unc_chisq <- safe_fm(fit_ml, "chisq")
      unc_p     <- safe_fm(fit_ml, "pvalue")

      if (verbose_flag) {
        reject_flag <- if (!is.na(unc_p) && unc_p < alpha) " *REJECT*" else ""
        cat(sprintf("    Result     : chi-sq = %8.2f, p = %.4f%s\\n",
                    ifelse(is.na(unc_chisq), NA, unc_chisq),
                    ifelse(is.na(unc_p), NA, unc_p),
                    reject_flag))
      }

      results[[idx]] <- data.frame(
        Model = model_key, N = n, Rep = i, iter_seed = global_seed,
        unc_chisq = unc_chisq, unc_p = unc_p,
        stringsAsFactors = FALSE
      )
    }

    if (verbose_flag) {
      partial <- bind_rows(results)
      partial_n <- partial[partial$N == n, ]
      rr_n <- mean(!is.na(partial_n$unc_p) & partial_n$unc_p < alpha, na.rm = TRUE) * 100
      cat(sprintf("\\n  >> N=%d complete: %d reps | Rejection rate = %.2f%%\\n", n, n_reps, rr_n))
    }
  }

  base_df_model <- bind_rows(results)
  saveRDS(base_df_model, paste0("thesis_sim_base_", model_key, ".rds"))
  cat(sprintf("\\n  [%s] BASE chunk complete: %d rows saved.\\n", info$name, nrow(base_df_model)))
  cat(sprintf("  Success: %d | Failed: %d | Rate: %.1f%%\\n\\n",
              success_count, fail_count, 100*success_count/(success_count+fail_count)))
}
```

## 2.2 Swain Correction

```{r sim-swain, results='hide'}
method_name <- "Swain"

for (model_key in names(models)) {
  info <- model_info[[model_key]]
  syn  <- info$syntax

  base_df <- readRDS(paste0("thesis_sim_base_", model_key, ".rds"))
  results <- list()
  success_count <- 0

  pb <- progress_bar$new(
    format = paste0("  [swain-", substr(model_key, 1, 4), "] ",
                    "[:bar] :percent | ETA: :eta | Iter :cur/:tot | N=:n | Rep :rep/:reps"),
    total = nrow(base_df), clear = FALSE, width = 80
  )

  for (row_idx in seq_len(nrow(base_df))) {
    row <- base_df[row_idx, ]
    pb$tick(tokens = list(cur = row_idx, tot = nrow(base_df),
                          n = row$N, rep = row$Rep, reps = n_reps))

    set.seed(row$iter_seed)
    sim_data <- tryCatch(simulateData(syn, sample.nobs = row$N), error = function(e) NULL)
    fit_ml   <- safe_fit(syn, sim_data, estimator = "ML")
    res      <- safe_smallN(fit_ml, "swain")

    if (!is.na(res$chisq)) success_count <- success_count + 1

    results[[row_idx]] <- data.frame(
      N = row$N, Rep = row$Rep,
      T_Swain = res$chisq, P_Swain = res$pvalue,
      stringsAsFactors = FALSE
    )
  }

  df_out <- bind_rows(results)
  saveRDS(df_out, paste0("thesis_sim_swain_", model_key, ".rds"))
  cat(sprintf("  [%s] %s chunk complete: %d rows. Successful extractions: %d/%d (%.1f%%)\\n",
              info$name, method_name, nrow(df_out), success_count, nrow(df_out),
              100*success_count/nrow(df_out)))
}
```

## 2.3 Bartlett Correction

```{r sim-bartlett, results='hide'}
method_name <- "Bartlett"

for (model_key in names(models)) {
  info <- model_info[[model_key]]
  syn  <- info$syntax

  base_df <- readRDS(paste0("thesis_sim_base_", model_key, ".rds"))
  results <- list()
  success_count <- 0

  pb <- progress_bar$new(
    format = paste0("  [bart-", substr(model_key, 1, 4), "] ",
                    "[:bar] :percent | ETA: :eta | Iter :cur/:tot | N=:n | Rep :rep/:reps"),
    total = nrow(base_df), clear = FALSE, width = 80
  )

  for (row_idx in seq_len(nrow(base_df))) {
    row <- base_df[row_idx, ]
    pb$tick(tokens = list(cur = row_idx, tot = nrow(base_df),
                          n = row$N, rep = row$Rep, reps = n_reps))

    set.seed(row$iter_seed)
    sim_data <- tryCatch(simulateData(syn, sample.nobs = row$N), error = function(e) NULL)
    fit_ml   <- safe_fit(syn, sim_data, estimator = "ML")
    res      <- safe_smallN(fit_ml, "bartlett")

    if (!is.na(res$chisq)) success_count <- success_count + 1

    results[[row_idx]] <- data.frame(
      N = row$N, Rep = row$Rep,
      T_Bart = res$chisq, P_Bart = res$pvalue,
      stringsAsFactors = FALSE
    )
  }

  df_out <- bind_rows(results)
  saveRDS(df_out, paste0("thesis_sim_bart_", model_key, ".rds"))
  cat(sprintf("  [%s] %s chunk complete: %d rows. Successful extractions: %d/%d (%.1f%%)\\n",
              info$name, method_name, nrow(df_out), success_count, nrow(df_out),
              100*success_count/nrow(df_out)))
}
```

## 2.4 Yuan (2015) Correction

```{r sim-yuan, results='hide'}
method_name <- "Yuan-2015"

for (model_key in names(models)) {
  info <- model_info[[model_key]]
  syn  <- info$syntax

  base_df <- readRDS(paste0("thesis_sim_base_", model_key, ".rds"))
  results <- list()
  success_count <- 0

  pb <- progress_bar$new(
    format = paste0("  [yuan-", substr(model_key, 1, 4), "] ",
                    "[:bar] :percent | ETA: :eta | Iter :cur/:tot | N=:n | Rep :rep/:reps"),
    total = nrow(base_df), clear = FALSE, width = 80
  )

  for (row_idx in seq_len(nrow(base_df))) {
    row <- base_df[row_idx, ]
    pb$tick(tokens = list(cur = row_idx, tot = nrow(base_df),
                          n = row$N, rep = row$Rep, reps = n_reps))

    set.seed(row$iter_seed)
    sim_data <- tryCatch(simulateData(syn, sample.nobs = row$N), error = function(e) NULL)
    fit_ml   <- safe_fit(syn, sim_data, estimator = "ML")
    res      <- safe_smallN(fit_ml, "yuan.2015")

    if (!is.na(res$chisq)) success_count <- success_count + 1

    results[[row_idx]] <- data.frame(
      N = row$N, Rep = row$Rep,
      T_Yuan = res$chisq, P_Yuan = res$pvalue,
      stringsAsFactors = FALSE
    )
  }

  df_out <- bind_rows(results)
  saveRDS(df_out, paste0("thesis_sim_yuan_", model_key, ".rds"))
  cat(sprintf("  [%s] %s chunk complete: %d rows. Successful extractions: %d/%d (%.1f%%)\\n",
              info$name, method_name, nrow(df_out), success_count, nrow(df_out),
              100*success_count/nrow(df_out)))
}
```

## 2.5 Satorra-Bentler (MLM Estimator)

```{r sim-sb, results='hide'}
method_name <- "Satorra-Bentler"

for (model_key in names(models)) {
  info <- model_info[[model_key]]
  syn  <- info$syntax

  base_df <- readRDS(paste0("thesis_sim_base_", model_key, ".rds"))
  results <- list()
  success_count <- 0

  pb <- progress_bar$new(
    format = paste0("  [SB-", substr(model_key, 1, 4), "]   ",
                    "[:bar] :percent | ETA: :eta | Iter :cur/:tot | N=:n | Rep :rep/:reps"),
    total = nrow(base_df), clear = FALSE, width = 80
  )

  for (row_idx in seq_len(nrow(base_df))) {
    row <- base_df[row_idx, ]
    pb$tick(tokens = list(cur = row_idx, tot = nrow(base_df),
                          n = row$N, rep = row$Rep, reps = n_reps))

    set.seed(row$iter_seed)
    sim_data <- tryCatch(simulateData(syn, sample.nobs = row$N), error = function(e) NULL)
    fit_mlm  <- safe_fit(syn, sim_data, estimator = "MLM")

    sb_chisq <- safe_fm(fit_mlm, "chisq.scaled")
    sb_pval  <- safe_fm(fit_mlm, "pvalue.scaled")

    if (!is.na(sb_chisq)) success_count <- success_count + 1

    results[[row_idx]] <- data.frame(
      N = row$N, Rep = row$Rep,
      T_SB = sb_chisq, P_SB = sb_pval,
      stringsAsFactors = FALSE
    )
  }

  df_out <- bind_rows(results)
  saveRDS(df_out, paste0("thesis_sim_sb_", model_key, ".rds"))
  cat(sprintf("  [%s] %s chunk complete: %d rows. Successful extractions: %d/%d (%.1f%%)\\n",
              info$name, method_name, nrow(df_out), success_count, nrow(df_out),
              100*success_count/nrow(df_out)))
}
```

## 2.6 Yuan-Bentler (MLR Estimator)

```{r sim-yb, results='hide'}
method_name <- "Yuan-Bentler"

for (model_key in names(models)) {
  info <- model_info[[model_key]]
  syn  <- info$syntax

  base_df <- readRDS(paste0("thesis_sim_base_", model_key, ".rds"))
  results <- list()
  success_count <- 0

  pb <- progress_bar$new(
    format = paste0("  [YB-", substr(model_key, 1, 4), "]   ",
                    "[:bar] :percent | ETA: :eta | Iter :cur/:tot | N=:n | Rep :rep/:reps"),
    total = nrow(base_df), clear = FALSE, width = 80
  )

  for (row_idx in seq_len(nrow(base_df))) {
    row <- base_df[row_idx, ]
    pb$tick(tokens = list(cur = row_idx, tot = nrow(base_df),
                          n = row$N, rep = row$Rep, reps = n_reps))

    set.seed(row$iter_seed)
    sim_data <- tryCatch(simulateData(syn, sample.nobs = row$N), error = function(e) NULL)
    fit_mlr  <- safe_fit(syn, sim_data, estimator = "MLR")

    yb_chisq <- safe_fm(fit_mlr, "chisq.scaled")
    yb_pval  <- safe_fm(fit_mlr, "pvalue.scaled")

    if (!is.na(yb_chisq)) success_count <- success_count + 1

    results[[row_idx]] <- data.frame(
      N = row$N, Rep = row$Rep,
      T_YB = yb_chisq, P_YB = yb_pval,
      stringsAsFactors = FALSE
    )
  }

  df_out <- bind_rows(results)
  saveRDS(df_out, paste0("thesis_sim_yb_", model_key, ".rds"))
  cat(sprintf("  [%s] %s chunk complete: %d rows. Successful extractions: %d/%d (%.1f%%)\\n",
              info$name, method_name, nrow(df_out), success_count, nrow(df_out),
              100*success_count/nrow(df_out)))
}
```

## 2.7 Combine All Results

```{r sim-combine}
all_results <- list()
model_counter <- 0

for (model_key in names(models)) {
  model_counter <- model_counter + 1
  info <- model_info[[model_key]]

  base_df  <- readRDS(paste0("thesis_sim_base_",  model_key, ".rds"))
  swain_df <- readRDS(paste0("thesis_sim_swain_", model_key, ".rds"))
  bart_df  <- readRDS(paste0("thesis_sim_bart_",  model_key, ".rds"))
  yuan_df  <- readRDS(paste0("thesis_sim_yuan_",  model_key, ".rds"))
  sb_df    <- readRDS(paste0("thesis_sim_sb_",    model_key, ".rds"))
  yb_df    <- readRDS(paste0("thesis_sim_yb_",    model_key, ".rds"))

  merged <- base_df %>%
    select(Model, N, Rep, unc_chisq, unc_p) %>%
    left_join(swain_df %>% select(N, Rep, T_Swain, P_Swain), by = c("N", "Rep")) %>%
    left_join(bart_df  %>% select(N, Rep, T_Bart, P_Bart),   by = c("N", "Rep")) %>%
    left_join(yuan_df  %>% select(N, Rep, T_Yuan, P_Yuan),   by = c("N", "Rep")) %>%
    left_join(sb_df    %>% select(N, Rep, T_SB, P_SB),       by = c("N", "Rep")) %>%
    left_join(yb_df    %>% select(N, Rep, T_YB, P_YB),       by = c("N", "Rep")) %>%
    mutate(
      Model_Name = info$name,
      Model_Desc = info$description,
      Model_DF   = info$df,
      Reject_Unc   = safe_reject(unc_p),
      Reject_Swain = safe_reject(P_Swain),
      Reject_Bart  = safe_reject(P_Bart),
      Reject_Yuan  = safe_reject(P_Yuan),
      Reject_SB    = safe_reject(P_SB),
      Reject_YB    = safe_reject(P_YB)
    )

  all_results[[model_key]] <- merged
  cat(sprintf("  [%d/%d] %s combined: %d rows.\\n", model_counter, length(models), info$name, nrow(merged)))
}

full_results <- bind_rows(all_results)
saveRDS(full_results, "thesis_simulation_raw_results.rds")
cat(sprintf("\\nTotal combined results: %d rows, %d columns.\\n",
            nrow(full_results), ncol(full_results)))
```

# 3. Analysis: Rejection Rates (Type I Error)

We calculate the proportion of replications where $p < 0.05$ for each combination of **Model Complexity**, **Sample Size**, and **Correction Method**. Since the data-generating model matches the fitted model, the expected rejection rate is $\\alpha = 0.05$ (5%).

## 3.1 Full Summary Table

```{r analysis-summary}
summary_table <- full_results %>%
  group_by(Model_Name, N) %>%
  summarise(
    Model_DF   = first(Model_DF),
    RR_Unc    = mean(Reject_Unc,   na.rm = TRUE) * 100,
    RR_Swain  = mean(Reject_Swain, na.rm = TRUE) * 100,
    RR_Bart   = mean(Reject_Bart,  na.rm = TRUE) * 100,
    RR_Yuan   = mean(Reject_Yuan,  na.rm = TRUE) * 100,
    RR_SB     = mean(Reject_SB,    na.rm = TRUE) * 100,
    RR_YB     = mean(Reject_YB,    na.rm = TRUE) * 100,
    .groups = "drop"
  )

# Display tables per model
for (model_key in names(models)) {
  info <- model_info[[model_key]]
  tbl <- summary_table %>%
    filter(Model_Name == info$name) %>%
    select(-Model_Name)

  cat(sprintf("\\n### %s (df = %d)\\n\\n", info$name, info$df))
  print(kable(tbl,
        digits = 2,
        caption = paste0("Type I Error Rates (Rejection %) for ", info$name,
                         ". Ideal rate = 5%."),
        col.names = c("N", "df", "Uncorrected", "Swain", "Bartlett",
                      "Yuan-2015", "Satorra-Bentler", "Yuan-Bentler")))
}
```

## 3.2 Large-Sample Validation (N >= 1000)

For large sample sizes, all methods should converge to approximately 5%. This serves as a validation check.

```{r analysis-large-n-check}
large_n_check <- summary_table %>%
  filter(N >= 1000) %>%
  group_by(Model_Name) %>%
  summarise(
    across(starts_with("RR_"),
           ~ sprintf("%.2f%%", mean(., na.rm = TRUE))),
    .groups = "drop"
  )
kable(large_n_check,
      caption = "Mean rejection rates at N >= 1000. All methods should be near 5%.")
```

# 4. Visualization of Results

## 4.1 Main Plot: Rejection Rates by Model Complexity and Sample Size

```{r plot-results, fig.width=14, fig.height=10}
plot_data <- summary_table %>%
  select(Model_Name, N, RR_Unc, RR_Swain, RR_Bart, RR_Yuan, RR_SB, RR_YB) %>%
  pivot_longer(cols = starts_with("RR_"),
               names_to = "Method", values_to = "RejectionRate") %>%
  mutate(Method = factor(Method,
                         levels = c("RR_Unc", "RR_Swain", "RR_Bart", "RR_Yuan",
                                    "RR_SB", "RR_YB"),
                         labels = c("Uncorrected LRT", "Swain (Bartlett)", "Bartlett (Gen)",
                                    "Yuan-2015", "Satorra-Bentler", "Yuan-Bentler")))

ggplot(plot_data, aes(x = N, y = RejectionRate, color = Method, group = Method)) +
  geom_line(linewidth = 1) +
  geom_point(size = 2) +
  geom_hline(yintercept = 5, linetype = "dashed", color = "black", linewidth = 0.5) +
  geom_ribbon(aes(ymin = 4.5, ymax = 5.5, fill = "Bradley Robust"),
              alpha = 0.15, color = NA, show.legend = TRUE) +
  scale_x_log10(breaks = sample_sizes) +
  scale_fill_manual(values = c("Bradley Robust" = "grey60"),
                    guide = guide_legend(override.aes = list(alpha = 0.3))) +
  facet_wrap(~ Model_Name, scales = "free_y", ncol = 1) +
  labs(title = "Type I Error Rates Across Model Complexity Levels",
       subtitle = "Dashed line = nominal alpha (5%); shaded band = Bradley's robust zone (4.5%--5.5%)",
       x = "Sample Size (Log Scale)",
       y = "Rejection Rate (%)",
       color = "Correction Method",
       fill = "") +
  theme_minimal() +
  theme(legend.position = "bottom",
        strip.text = element_text(face = "bold", size = 12))
```

## 4.2 Focused Plot: Small Sample Sizes (N <= 300)

```{r plot-small-n, fig.width=14, fig.height=10}
plot_small <- plot_data %>%
  filter(N <= 300)

ggplot(plot_small, aes(x = N, y = RejectionRate, color = Method, group = Method)) +
  geom_line(linewidth = 1.2) +
  geom_point(size = 2.5) +
  geom_hline(yintercept = 5, linetype = "dashed", color = "black") +
  geom_ribbon(aes(ymin = 4.5, ymax = 5.5), alpha = 0.15, fill = "grey60", color = NA) +
  facet_wrap(~ Model_Name, scales = "free_y", ncol = 1) +
  labs(title = "Type I Error Rates at Small Sample Sizes (N <= 300)",
       subtitle = "Where small-sample corrections matter most",
       x = "Sample Size",
       y = "Rejection Rate (%)") +
  theme_minimal() +
  theme(legend.position = "bottom",
        strip.text = element_text(face = "bold", size = 12))
```

## 4.3 Method Comparison at Key Sample Sizes

```{r plot-bar-comparison, fig.width=14, fig.height=10}
key_ns <- c(50, 100, 200, 300)

bar_data <- summary_table %>%
  filter(N %in% key_ns) %>%
  select(Model_Name, N, RR_Unc, RR_Swain, RR_Bart, RR_Yuan, RR_SB, RR_YB) %>%
  pivot_longer(cols = starts_with("RR_"),
               names_to = "Method", values_to = "RejectionRate") %>%
  mutate(Method = factor(Method,
                         levels = c("RR_Unc", "RR_Swain", "RR_Bart", "RR_Yuan",
                                    "RR_SB", "RR_YB"),
                         labels = c("Uncorrected", "Swain", "Bartlett", "Yuan-2015",
                                    "Satorra-Bentler", "Yuan-Bentler")),
         N = factor(N))

ggplot(bar_data, aes(x = Method, y = RejectionRate, fill = Method)) +
  geom_col(alpha = 0.8) +
  geom_hline(yintercept = 5, linetype = "dashed", color = "red", linewidth = 0.8) +
  geom_hline(yintercept = c(4.5, 5.5), linetype = "dotted", color = "darkgrey", linewidth = 0.5) +
  facet_grid(Model_Name ~ N) +
  labs(title = "Rejection Rates at Key Sample Sizes",
       subtitle = "Red dashed line = nominal alpha (5%); grey dotted = Bradley's robust bounds (4.5% & 5.5%)",
       x = NULL, y = "Rejection Rate (%)") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1, size = 7),
        legend.position = "none",
        strip.text = element_text(face = "bold"))
```

# 5. Model Complexity Comparison (Bradley's Criterion Only)

This section directly addresses **Question 1**: How does model complexity affect the performance of small-sample corrections?  
Evaluation is performed **exclusively** via Bradley's (1978) robust zone: a method is classified as **robust** if its empirical rejection rate falls within 4.5%--5.5%.

## 5.1 Rejection Rate Heatmap with Bradley Deviation

```{r plot-heatmap, fig.width=14, fig.height=10}
small_n_table <- summary_table %>%
  filter(N <= 500) %>%
  select(Model_Name, N, RR_Unc, RR_Swain, RR_Bart, RR_Yuan, RR_SB, RR_YB) %>%
  pivot_longer(cols = starts_with("RR_"),
               names_to = "Method", values_to = "RR") %>%
  mutate(
    Method = factor(Method, levels = c("RR_Unc", "RR_Swain", "RR_Bart", "RR_Yuan",
                                        "RR_SB", "RR_YB"),
                    labels = c("Uncorrected", "Swain", "Bartlett", "Yuan-2015",
                               "Satorra-Bentler", "Yuan-Bentler")),
    N = factor(N),
    Model_Name = factor(Model_Name, levels = sapply(model_info, function(x) x$name)),
    Deviation = RR - 5,
    Bradley_Class = case_when(
      RR >= 4.5 & RR <= 5.5 ~ "Robust",
      RR < 4.5 ~ "Conservative",
      RR > 5.5 ~ "Liberal",
      TRUE ~ "NA"
    ),
    Label_Color = ifelse(Bradley_Class == "Robust", "darkgreen", "black")
  )

ggplot(small_n_table, aes(x = Method, y = N, fill = Deviation)) +
  geom_tile(color = "white") +
  geom_text(aes(label = sprintf("%.1f", RR), color = Label_Color), size = 2.8) +
  scale_fill_gradient2(low = "steelblue", mid = "white", high = "firebrick",
                       midpoint = 0, limits = c(-5, 20),
                       name = "Deviation\\nfrom 5%") +
  scale_color_identity(guide = "none") +
  facet_wrap(~ Model_Name, ncol = 1) +
  labs(title = "Rejection Rate Heatmap: Model Complexity x Method x Sample Size",
       subtitle = "Values in cells = rejection rate (%). Dark green text = inside Bradley's robust zone.",
       x = "Correction Method", y = "Sample Size") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1, size = 9),
        strip.text = element_text(face = "bold", size = 12),
        legend.position = "right")
```

## 5.2 Bradley Robust Zone Classification

For each combination of Model and N, identify which method(s) fall within Bradley's (1978) robust zone (4.5%--5.5%).

```{r bradley-classification}
bradley_table <- summary_table %>%
  select(Model_Name, N, RR_Unc, RR_Swain, RR_Bart, RR_Yuan, RR_SB, RR_YB) %>%
  pivot_longer(cols = starts_with("RR_"),
               names_to = "Method", values_to = "RR") %>%
  mutate(
    Method = factor(Method, levels = c("RR_Unc", "RR_Swain", "RR_Bart", "RR_Yuan",
                                        "RR_SB", "RR_YB"),
                    labels = c("Uncorrected", "Swain", "Bartlett", "Yuan-2015",
                               "Satorra-Bentler", "Yuan-Bentler")),
    Bradley_Class = case_when(
      is.na(RR) ~ "NA",
      RR >= 4.5 & RR <= 5.5 ~ "Robust",
      RR < 4.5 ~ "Conservative",
      RR > 5.5 ~ "Liberal"
    )
  )

# For each model x N, count how many methods are robust
robust_count <- bradley_table %>%
  filter(!is.na(RR)) %>%
  group_by(Model_Name, N) %>%
  summarise(
    Robust_Methods = sum(Bradley_Class == "Robust"),
    Liberal_Methods = sum(Bradley_Class == "Liberal"),
    Conservative_Methods = sum(Bradley_Class == "Conservative"),
    Total_Methods = n(),
    .groups = "drop"
  ) %>%
  mutate(Robust_Pct = Robust_Methods / Total_Methods * 100)

kable(robust_count,
      digits = 1,
      caption = "Number of methods within Bradley's robust zone by Model and Sample Size.",
      col.names = c("Model", "N", "Robust", "Liberal", "Conservative",
                    "Total", "Robust %"))

# Also show the detailed classification matrix
cat("\\n\\n### Detailed Bradley Classification by Model\\n\\n")

for (model_key in names(models)) {
  info <- model_info[[model_key]]
  cat(sprintf("\\n#### %s (df = %d)\\n\\n", info$name, info$df))

  class_matrix <- bradley_table %>%
    filter(Model_Name == info$name) %>%
    select(N, Method, Bradley_Class) %>%
    pivot_wider(names_from = Method, values_from = Bradley_Class)

  print(kable(class_matrix,
        caption = paste0("Bradley classification per method for ", info$name, ".")))
}
```

## 5.3 Interaction Plot: Method Performance Across Model Complexities

This plot directly shows how each correction method's performance changes as model complexity increases, using Bradley's zone as the reference.

```{r plot-interaction, fig.width=12, fig.height=8}
interaction_data <- summary_table %>%
  filter(N %in% c(50, 100, 150, 200, 300)) %>%
  select(Model_Name, N, RR_Unc, RR_Swain, RR_Bart, RR_Yuan, RR_SB, RR_YB) %>%
  pivot_longer(cols = starts_with("RR_"),
               names_to = "Method", values_to = "RR") %>%
  mutate(
    Method = factor(Method, levels = c("RR_Unc", "RR_Swain", "RR_Bart", "RR_Yuan",
                                        "RR_SB", "RR_YB"),
                    labels = c("Uncorrected", "Swain", "Bartlett", "Yuan-2015",
                               "Satorra-Bentler", "Yuan-Bentler")),
    N = factor(N),
    Model_DF = case_when(
      Model_Name == model_info$simple_cfa$name  ~ model_info$simple_cfa$df,
      Model_Name == model_info$complex_cfa$name ~ model_info$complex_cfa$df
    )
  )

ggplot(interaction_data, aes(x = Model_DF, y = RR, color = Method, group = Method)) +
  geom_line(linewidth = 1.2) +
  geom_point(size = 3) +
  geom_hline(yintercept = 5, linetype = "dashed", color = "black") +
  geom_hline(yintercept = c(4.5, 5.5), linetype = "dotted", color = "darkgrey") +
  facet_wrap(~ N) +
  labs(title = "Method Performance Across Model Complexities",
       subtitle = "X-axis = model degrees of freedom (higher = more complex). Dashed = 5%; dotted = Bradley bounds.",
       x = "Model Degrees of Freedom",
       y = "Rejection Rate (%)",
       color = "Correction Method") +
  theme_minimal() +
  theme(legend.position = "bottom",
        strip.text = element_text(face = "bold"))
```

# 6. Session Info

```{r session-info, echo=TRUE}
sessionInfo()
```
